---
title: "CookBook"
output: md_document
---
This is project for Coursera getdata-011 course.



## Load libraries

```{r}
library(tidyr)
library(dplyr)
library(reshape2)
```

## Set working directory and Read data files

```{r}
setwd("E://Projects//R//getdata-011//as1//UCI HAR Dataset")
d_Act_Test  <- read.table( "test//Y_test.txt"   ,header = FALSE)
d_Act_Train <- read.table( "train//Y_train.txt" ,header = FALSE)
d_Sub_Test  <- read.table( "test//subject_test.txt"   ,header = FALSE)
d_Sub_Train <- read.table( "train//subject_train.txt" ,header = FALSE)
d_Feat_Test <- read.table( "test//X_test.txt"  ,header = FALSE)
d_Feat_Train <- read.table("train//X_train.txt",header = FALSE)
d_Feat_Names <- read.table("features.txt",header = FALSE)
Act_Labels   <- read.table("activity_labels.txt",header = FALSE)
```


# 1. Merges the training and the test sets to create one data set

```{r}
d_Act <- rbind(d_Act_Test,d_Act_Train)
d_Sub <- rbind(d_Sub_Test,d_Sub_Train)
d_Feat <- rbind(d_Feat_Test,d_Feat_Train)

rm(list=c("d_Act_Test","d_Act_Train","d_Sub_Test","d_Sub_Train","d_Feat_Test","d_Feat_Train"))
```

## Add column names

```{r}
names(d_Act)  <- c("Activity")
head(d_Act)
names(d_Sub)  <- c("Subject")
head(d_Sub)
names(d_Feat) <- d_Feat_Names[,2]
names(d_Feat)
names(Act_Labels) <- c("Activity","ActivityName")
head(Act_Labels)
```
# 2. Extracts only the measurements on the mean and standard deviation for each measurement

```{r}
d <- d_Feat[,grep("mean\\(\\)|std\\(\\)",d_Feat_Names[,2])]
names(d)
```

## Marge data by comlumns

```{r}
d <- cbind(d,d_Sub,d_Act)
names(d)
rm(list=c("d_Feat","d_Sub","d_Act","d_Feat_Names"))
```

# 3. Uses descriptive activity names to name the activities in the data set

```{r}
d <- merge(x=d,y=Act_Labels,by="Activity")
str(d)
```

# 4. Appropriately labels the data set with descriptive variable names. 


Rename columns:  
. t -> time  
. f -> frequency  
. Acc -> Accelerometer  
. BodyBody -> Body  
. Gyro -> Gyroscope  
. Mag -> Magnitude  


```{r}
names(d)<-gsub("^t", "time", names(d))            # t -> time
names(d)<-gsub("^f", "frequency", names(d))       # f -> frequency
names(d)<-gsub("Acc", "Accelerometer", names(d))  # Acc -> Accelerometer
names(d)<-gsub("BodyBody", "Body", names(d))      # BodyBody -> Body
names(d)<-gsub("Gyro", "Gyroscope", names(d))     # Gyro -> Gyroscope
names(d)<-gsub("Mag", "Magnitude", names(d))      # Mag -> Magnitude
str(d)
```

# 5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

Convert to long format
```{r}
d_rows <-  melt(d, id=c("Activity","ActivityName","Subject"))
names(d_rows)
```
Compute means
```{r}
d_avg  <-  dcast(data = d_rows, formula = Activity+ActivityName+Subject~variable, fun.aggregate = mean)
names(d_avg)
```

## Write the file

```{r}
write.table(x = d_avg, file = "Dataset_out.txt", row.names = FALSE)
```

## END

